\chapter{Epistemology}
“Epistemology without contact with science becomes an empty scheme. Science without epistemology is… primitive and muddled.” — Albert Einstein

\section{Introduction}
Here we will derive the basic principles of Epistemology that will later be expanded upon by the next chapter on the philosophy of science.

\subsection{Statements}

There are so many possible statements one can make \emph{"an electron is 511 $\pm$ 0.5 keV"} or \emph{"I am a person"} or \emph{brutalism is the
best form of artwork}. Given that these statements will be at the corners stone of the structure and development of knowledge; clear definitions, rules,
and such must be derived.

One assumption one can take is that these statements exist within the Boolean domain thus that $S \in \mathbb{B} = {FALSE, TRUE}$. Making it so that not
only can truth values be assigned to a statement, a statement can only be true or false. This is clear from any logical analysis that for their to be
a logically consistent truth system, that their only be true or false. Nuance, while useful outside of strict epistemology, doesn't actually change
the fact that the statement is either true or false.

From here, the rules developed in Formal logic ring true. Addition, negation, or, etc. They are the rules that govern these statements and allow for
knowledge to be constructed in the first place.

Another rule to add is equivalence, but there are different types of equivalence. Semantic equivalence(saying the same thing in a different form),
Logical equivalence(One proves another, or both prove each other), and finally material equivalence(they both have the same truth value). These tools of
equivalence will be useful in the future.

An addition to traditional logic are adding relations like narrower, broader, compatible, or incompatible.

With these in mind we satisfy De Morgan Laws and Boolean algebra infinite distribution with all of the rules we need for the construction of statements.
Other similar methods can be used, but this minimal set traditionally holds.

\section{Verifying Statements}

Now we must talk about how to verify these statements for the development of knowledge.
\subsection{Deduction}

Using the principles of formal logic, one may derive statements from one another. These statements will be sound by definition but not
technically true by definition. For they rely on the statements, Axioms, taken to be true.

These rules must be furfiled by how we defined a statement to be. Being Boolean and thus susceptible to the relations of formal logic.

This brings us to the end, very little knowledge can be gained based upon the limited axioms we have already developed(much of this knowledge has already
been explored).

\subsection{Induction}

This brings us to our next form of developing logic, induction. From our earlier Axiom of UoN(uniformity of Nature), induction arises. Allowing us to
use past observations to inform natural laws and models. Finding that predictive power is evidence for the validity of a model. There are other rules and
ideas combined with this that will be addressed in the following chapter.

There is also abduction which is closely combined with induction, this will also be addressed in the next chapter.
