\section{Assumptions of Physics}

\subsection{Overview}
The overall goal is to explore the minimal set of physical assumptions are necessary and sufficient to derive different theories within a
unified framework. This is almost identical to my Axiom project with the exeption that while not as broad their research is much deeper than mine.

It is broken into two parts

\textbf{Reverse Physics}: Looks at the main theories and finding the common and the different aspects of those theories.

\textbf{Physical Mathematics}: Connecting physical objects and theories to be mapped onto the correct mathematical objects



\subsection{Reverse Physics}

It was a great read with a lot of interesting ideas, but I don't want to write it all, esspecially since I am planning on writing something very
similar in part 1.

So, I will write a summary of the summary

The first assumption is Infinitesimal Reducibility(IR). This tells us the domain of classical physics is of those that can be thought of as made of
arbitrarily small parts. Mathematically this tells us that the state space of the particles is a differentiable manifold, together with a volume measure
that defines the count of states for each region. We can then add the assumption IND that tells us that the system is decomposable into independent
degrees of freedom. For this to work the manifold must have even dimensions. That any state variable $q^i$ has a conjugate state $p_i$. This give
a symplectic manifold. If we assume DR, that evolution is deterministic and reversable, we obtain Hamiltonian Mechanics. This enforces preservation of
area.Thus, the displacement vector field is \emph{H}, which corresponds with the Hamiltonian. This can be generalized to the time dependent case, which
recovers relativistic features even without the noting of a metric tensor.

Assuming KE, that dynamics are recoverable from kinematics, we get Newtonian. If we assume both KE and DR we get Lagrangian.

\subsection{Physical Mathematics}
This one is a bit more abstract and newer stuff, so I will have more notes.
