\chapter{Bible Reading}

\section{2026-16-02}
\subsection{Genesis 41:17-42:17}

God protects Joseph through establishing gifts within him. He does the same for us.

Why does Joseph test his brothers?
\subsection{Matthew 13:24-46}

The parables of Jesus, establish stories and myth as the methodology of developing the abstract concepts of God's will.

It refers to the weeds as everything that causes sin and all who do evil, what exactly does this mean? Everyone does evil and
everyone has within that which tempts them. Taking out the ``weeds'' prematurely will destroy the wheat.

The final stories is about how the kingdom of God gives everything for the grace of those who are lost.
\subsection{Psalm 18:1-15}
Love of God
\subsection{Proverbs 4:1-6}
Community, family, and God fosters wisdom. Wisdom that protects you.


\section{2026-17-02}
\subsection{Old testament}
Why is Joseph testing with them even after hearing what they had to say while also giving them money
\subsection{New Testament}
The kingdom of God takes in all, but not all remain.

Interesting how such a radical take on ones word is used.
\subsection{Psalm}
God rescues you and protects you from the enemies that are greater than you
\subsection{Proverbs}
Pursue wisdom over all other virtues



\section{2026-24-03}
\subsection{Genesis 46:1-47:31}
Joseph built his family and tradition up in accordance with God's will. He also did his duty with extreme diligence.

\subsection{Matthew 15:1-28}
While tradition matters, God's commandments are far above.

Your words matter and define you. Disregarding this defiles your nature. Acting in a virtuous manner in accordance with the idea matters much more than
rules. Beyond that, a critical examination of such things is important as people lead one another astray.

Actions can corrupt you, they are not in isolation but rather, not just a consequence of what is beneath but create what is beneath.

Jesus was here for the Jewish people, yet his words go far beyond.

\subsection{Psalm 19:1-14}
To be truly free is to be free of sin, while this is impossible on Earth, God's commands lead to this by our creation of our own self though the actions
he has put forth.

\subsection{Proverbs 4:14-19}
Don't think of evil for it will corrupt you without thought. For, while not always, that is what evil comes from, lack of thought. Impulse and action
without conscious morality driving ones will. One must then separate oneself from this evil that surrounds them.


\section{03/25/26}
\subsection{Genesis 48:1-49:33}
I continually attempt to find greater understanding of God's will for us through the
traditions and things he set forth. How should I go about doing it? I mean I would
make the claim being an endogamous clan based family structure does not hold
deeper wisdom, but how do I make sure my cultural preferences are hidding things from me in other areas.

In this story as in others, God overturns natural human hierarchy as he choices the secondborn above the first.

In the prophecies it mentions the children's clans fate that mirror their temperament, flaws, and virtues. Meaning or fate is either our own or God has put it in fornt of us
purposefully.

Juda's past is messy but he brings out the Davidic monarchy and eventually Jesus.

Joseph's blessing begins by his attack but also being saved through God, not himself.

\subsection{Matthew 15:29-16:12}
Interpret the signs of our time to understand God's will.

Those that have turned for Jesus will need signs to see, but with those with faith that is not needed.

The Pharisees only offer short 'bread' coming from gratification of tradition and lineage, to go beyond one must follow Jesus.

The disciple worry about food even after seeing the miracle Jesus had just done. In the same way we so simply forget and ignore the acts Jesus has already done for us.

\subsection{Psalm 20:1-9}
To quickly we think our victories are our own, to devote ourself to Christ is the antidote to this pride.

\subsection{Proverbs 4:20-22}
Pay attention to the wisdom of others, especially what God says. Attempt to fully understand it, beyond even what they have defined for the wisdom.

Guard your heart tightly, even listening to the world around you too closely can corrupt you. This heart, the virtue inside of you guides your entire being, your life in ways that aren't clear at first glance. Sacrificing this is far more dangerous than it seems.

Even something a trivial as degrading language can have a profound impact on our heart, for this reason one must make a plan and follow it.

\subsection{Take-away}
I have already started on my essays on self-authorship, these passages even more so highlight how important this is for my development with my relationship with Christ.

\section{January 25}
\subsection{Genesis}
"Am I God, that I can punish you?" Only God has the right and capacity to punish in a just manner.

One theory I had was that they misunderstood years and that is why they lived so "long," but according to the bible they legtitamtely lived to see multiple generations worth of people.

\subsection{Matthew}
The disiples were told that Jesus would raise himself from the grave and Jesus even talked of the cross, and yet they doubted when the time came. We can too miss what is directly in front of us.

Peter tried to control Jesus even knowing he is the son of man, just as we do without thought.

What does Jesus mean by Peter is the Rock, why does he have this authority. What does it mean for God to give the authority over heaven to a mortal man and a singular one at that?

\subsection{Psalm}
We do not have enemies for victories, we only have reflections of God's. His victories is our honor, his enemies are ours. We are extensions of his will upon the Earth, empty without his will and might.

\subsection{Proverbs}
You will express the wisdom you have gained. While one can fake wisdom through prideful intellect, it becomes obvious over time as it falls as poision to the mind of those who hear.
