\chapter{Preface}
"If you start with the right axioms, the rest will follow."— David Hilbert
\singlespacing 
This book "Axiom" is a continuation of my previous project Lógos. Which was mostly a collection of essays on several topics; physics, philosophy, religion, civilization, psychology, personal plans, etc.

It was previously meant to work through my ideas, using the fact I was writing it out. It allowed me to keep track of the dozens of ideas and how they all interacted with each other. Developing on the complexity without forgetting and creating a full framework with defined axioms. 

Creating this new project is for multiple reasons. 
\begin{enumerate}
    \item To create a more organized book
    \begin{itemize}
        \item What I mean is have an order, like create a fully formalized epistemology and basic metaphysics and then using that to create a fully organized Ontology. Rather than a chaotic coll
    \end{itemize}
    \item To mark the end of my high school career and beginning of University
    \item Lógos had become too big and had too many errors
    \begin{itemize}
        \item Too big to run on Overleaf, too many errors to run directly in the terminal. 
        \begin{itemize}
            \item This will start smaller, and once it is bigger will be made without errors so it can be run on the terminal once it gets bigger. Also more modular 
    \end{itemize}
    \end{itemize}
    \item Be able to rewrite with my new knowledge to update it.
    \item Write it with a better understanding of the packages, LaTeX, and even create my own custom packages
\end{enumerate}
In the end, it serves the same purpose; to help me better understand things through writing, develop thing iteratively over time using writing, and write out notes to remember things for the future.

As of writing this section, the text will be broken into three parts. Part one being ''The Foundation." It would be a axiomatic approach to creating the foundations needed for future systems. Two, being ''Notes" on things that I have learned. Three, being writings on my ''Projects"; mostly physics research projects but also projects in further developing philosophy or other similar things. Finally, ''Life in Practice" being more practical things; plans for the future, self-analysis, ideals on society, etc.
