\chapter{Post-Surgery}
\section{Overview}

\section{1/9/2026 Essay: Cultivation in Degregation}

As mentioned in previous chapters, the development of virtue stands at the cornerstone of the existence of man. Thus, how to develop it is key.

The question of how to develop virtue, what virtues to develop, etc; differ from person to person. I will focus on myself for this essay, on a practical development, rather than in the abstract general
way I would traditionally go for.

Specifically, I will focus on my recent 'degregation' in many fields. What I mean is I have been struggling with health problems that caused constant pain, nausea, and brain fog.
To combate this I used "quick" and "automatic" gratification. Watched lots and lots, of Instagram videos and YouTube shorts. With quick and simple comedy TV in the background.
While it is difficult to divide what is caused by using these simple causes of gratification and what is caused by my still recovering body, but I am having trouble focusing, get tired easily,
less intrinsically motivated, and other similar malignities.

I have a belief that a person can create themselves based upon their habits. Thus, that is what I design to do, create myself in the image of my highest
values. I desire that I am someone who enjoys challege for it own sake(especially intellectual challenge), persistent high energy, optimistic outlook,  pro-social tendencies,
high focus, and the continual push towards greater virtue in all fields of life.

To reach these goals I have decided to pick up “The Karamazov Brothers,” a book I had abandoned earlier due to my declining condition. I did this not only for enjoyment, but to accomplish my goal. To slowly focus my mind on something that lasts longer than a minute, to remind myself of my enjoyment of intellectual type activities and engage my mind in something that could challenge it, and to reconnect myself with my faith.

I  am also reading “Numerical Hamiltonian Problems,” trying to learn to code a website, code personal pet projects, watch educational and long-form youtube videos rather than shorts, exercise each day, and write each day. I do all of these things to re-develop my attention, enjoyment of effort, regain my energy, and to develop my skills.

Developing myself on the social side of things is a bit more challenging. Currently as of writing this essay I am still isolated from my peers, but I have a plan. Teaching Sunday school, volunteering for church outreach groups, returning to my scout troop, participating in JROTC volunteer activities, teaching karate, and so much more. Things to redevelop my enjoyment and understanding of social responsibilities and natural altruism.

With this current plan in motion, I will start making purposeful and willful actions in order to develop in the way that I design.

\section{2/16/2026: An alien unto myself}
