\chapter{Personal Philosophy}
"Only through the radical examination of one's own life and the reality surrounding may one gain authority over it. Through such authority their own happiness becomes clear. To have the freedom to be responsible for themselves and the integrity of their own mind. This is the principle and highest form of human action, to divine their own morality and values then shape themselves and reality into the image of their highest values.” | AJ Cason
\section{*God as Foundation}
\section{Will as Identity}
\par All throughout history, the question of identify has been constant. Who we are: are we are personality, outward actions, inward thoughts, natural impulses, cognitive style?
\par I propose a different method, we are our will. That is our method of identity. This proposition has many consequences.
\par Before I get to that, I must define your will. Your will is your highest self within you, that which pushes you to your highest ideals. The image that burns within you of what you could become, that whispers how you may achieve it. That is your will, your will to your own power over yourself.
\par First, it allows acting through purpose to be acting authentically. Many people find paradox between our need to live 'authentically'(a moronic ideal) and fulfilling their purpose and duty to others and themselves. Though, from my view these are the same. To act and bend your personality to your personal will, to fulfill your duty, isn't unauthentic, but rather the purest form of authenticity.
\par To 'act' and author yourself is your responsibility as a human, a creation of God the most high that has been made in his image as a being with a conscious mind. Don't live passively letting your whims and childhood define you, but rather your will is your definition.
\par Second, a devotion to your will is your  responsibility. To 'falter' is to kill yourself and let a husk(personality, impulses, etc_ take the place of the human mind that God has put within you. To let the flesh control you is dishonorable, evil, disgusting, and never to be considered. It is not understandable, it is not acceptable, never surrender, never compromise against anything beyond your will.
\par This can be observed through giving up, compromising, complaining, etc. These are evils. People seem to accept complaining as a natural reaction to 'unfairness' and that you are nothing more than your "childhood traumas," don't become this subhuman husk. Become more, become a thinking human.
\par Four, to let others to your thinking for you is to outsource your soul. To degenerate God's creation. Think for yourself, think logically and analytically, derive your 'first principles' clearly.
\section{*Fanatical Ethics}
\section{The Duty as an Actor}
\par As mentioned in "Will as Identity" you must in a sense become an "actor" in your life. What I mean by this is that you must control your reactions(be civilized and dignified) to fulfill your duty.
\par Be cheerful within the misk of irksome tasks and weighty responsibilities, hold your head up high, never complain, don't profane what is sacred, and so much more.
\par One, through "acting" you will become that in which you pursue, virtuous. You will become happy, become moral, become dignified, become who your will decides you must be. It is through this "act" you will become that image of your highest self within you.
\section{*The Aesthetic Pursuit of Truth}
