\chapter{Self-Authorship}
\begin{quote}
insert here
\end{quote}

\section{Scope and Understanding}

It has always been a clear belief of mine that it is a persons duty and responsibility to define themselves though conscious thought and action.
It has been something on the forfront of my mind. As mentioned in an earlier chapter on post-surgery and sicknesses, I haven't been the person I
used to be.

Regardless it is a very important thing to be done. To clearly define the virtues that define how I should live my life and then make sure
that I live in accordance to them.

I will begin defining who I want to be, much of it has already been defined in ethics, but personal ethics will be defined as well. Then, I will look
into actions I can take.

\section{Ideals of Becoming}

\subsection{Overview of Virtues}
In becoming I define a set of categories of virtues that will be further defined.
\begin{list}{Virtues}{}
    \item Intellectual
    \item Volitional
    \item Executive
    \item Stability
    \item Adaptive
    \item Social
\end{list}
While these are not equal categories nor exhaustive, they work as a good way to organize these essays for now.

\paragraph{Intellectual Virtues}

To be able to create oneself, one must be conscious of how to do so and who one wants to be. Some underlying things must be true.

I believe that someone(me) should have a world-view. One that is completely consestaint, that brokers all areas, and is useful for further creation.
A person should not simply listen vapidly and repeat the words of others without clear thought, but must have a formalized system to be able to not
simply add information but be capable of sythesising it and using it in a broader context. To have a rigorous view on everything and logic behind it.
This is the only true way to actually learn and function, without it you are simply repeating others with the variations of subconscious bias.

One must also have clear meta-cognitive skills, to question oneself it the only way to clearly understand something. While this can become natural
through rigour, developing the natural tendency may speed of the process without formal rigour at every turn.

Knowledge and understanding is incredibly important. To use, develop oneself in the abstract sense, and to be able to abstract for future knowledge.

The ability to abstract things to develop clearer understanding of it or relating systems. Always look for the underlying mechanism beneath, not
simply the begining and top and leave.

Humility to understand that which is beyond.

I want to be someone in constant though, of ethics, social responisbility, understanding the world around me. While maybe not the best desicion, it is mine.

Also, have your ideas be your own, fit them within your formal world-view and build upon them.
